---
title: |
       | Supplementary Materials for "Responses to Foreign Shaming over Climate Policy among Nationalist"
author: 
- "Matias Spektor[^spektor]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Guilherme N. Fasolin[^fasolin]"
date: November 15, 2020
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

\appendix

[^spektor]: Associate Professor, School of International Relations, Fundação Getulio Vargas, Brazil. Contact: <matias.spektor@fgv.br>, <https://www.matiasspektor.com/>.

[^mignozzetti]: Visiting Assistant Professor, Department of Quantitative Theory and Methods, Emory University. Contact: [umberto.mignozzetti@emory.edu](mailto:umberto.mignozzetti@emory.edu), <http://umbertomig.com>.

[^fasolin]: Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil. Contact: <guilherme.fasolin@fgv.br>, <https://github.com/GuilhermeFasolin>.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

#####
## Initializing
#####

# Start
rm(list=ls())

# R CRAN
r <- getOption("repos")
r["CRAN"] <- "http://cran.us.r-project.org"; options(repos = r)

# Install required packages
pkgs <- c('tidyverse', 'readxl', 'stringr', 
          'lmtest', 'sandwich', 'stargazer',
          'haven', 'survey', 'GDAtools',
          'weights','knitr','broom','gtools',
          'huxtable', 'compareGroups', 'lfe',
          'kableExtra', 'interplot', 'gridExtra',
          'miceadds', 'ggpubr', 'car')

installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T)
} 
invisible(lapply(pkgs, installIfNot))

# Load packages
invisible(lapply(pkgs, require, character.only = T))
rm(pkgs, installIfNot, r)

# Load datasets
load('data/environmental.RData')
```

\newpage

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

# Analysis Wave One \label{sec:w1}

## Descriptive Statistics

In the wave 1 dataset (`wave1` R object), we have the following variables:

1. **`nquest`**: 9-digit DataFolha Respondent Code.
2. **`female`**: Dummy for Female Respondent.
3. **`age`**: Age.
4. **`religion`**: 4-brackets religion levels.
5. **`evang`**: Dummy for Evangelical respondent.
6. **`income`**: Income levels.
7. **`more5mw`**: Respondent More than five minimum wage salaries.
8. **`hsmore`**: Dummy for High School or more of education.
9. **`outcbin`**: Dummy for support for governmental environmental decision.
10. **`trsource`**: Treatment status denoting the source of the foreign shaming.
11. **`trgovresp`**: Treatment status denoting government response to the foreign shaming. 
12. **`trstatus`**: Treatment status as appeared in the survey instrument.
13. **`natscale`**: National attachment scale.
14. **`region`**: Brazilian region.
15. **`wts`**: Weights computed by the DataFolha Institute.

Our analysis comes from a sample of `r dim(wave1)[1]` Brazilian administered in January 2020 by the Datafolha Institute as part of a larger, unrelated omnibus survey. We provide a detailed explanation about the sampling methodology in the APSA Experimental Report section of this appendix. Table \ref{tab1w1ds} shows the demographic characteristics of our sample.

```{r}
aux <- wave1 %>%
  dplyr::select(age, female, income, region,
                hsmore, religion,
                natscale) %>%
  rename(`Age` = age,
         `Female` = female,
         `Income` = income,
         `Region` = region,
         `High School or more` = hsmore,
         `Religion` = religion,
         `National Attachment Scale` = natscale)
```

```{r, results='hide'}
export2latex(
  descrTable(~., 
             digits = 2, 
             show.p.overall = F, 
             show.all = T, 
             data = aux)
)
```

\pagebreak

\begin{longtable}{lcc}
\caption{Sample Characteristics}\label{tab1w1ds}\\
\hline  
&     [ALL]     & \multirow{2}{*}{ N  }\\ 
&    N=2001     &      \\ 
\hline
\hline     
\endfirsthead 
\multicolumn{3}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
\hline
&     [ALL]     & \multirow{2}{*}{ N  }\\ 
&    N=2001     &      \\ 
\hline
\hline  
\endhead   
\hline
\multicolumn{3}{l}{\textit{continued on next page}} \\ 
\endfoot   
\multicolumn{3}{l}{}  \\ 
\endlastfoot 
Age & 42.96 (16.15) & 2001\\ 
Female: &               & 2001\\ 
$\qquad$No & 951 (47.53\%)  &     \\ 
$\qquad$Yes & 1050 (52.47\%) &     \\ 
Income: &               & 1899\\ 
$\qquad$BRL 0.00 to BRL 998.00 & 397 (20.91\%)  &     \\ 
$\qquad$BRL 999.00 to BRL 1,996.00 & 426 (22.43\%)  &     \\ 
$\qquad$BRL 1,997.00 to BRL 2,994.00 & 380 (20.01\%)  &     \\ 
$\qquad$BRL 2,995.00 to BRL 4,990.00 & 345 (18.17\%)  &     \\ 
$\qquad$BRL 4,991.00 or more & 351 (18.48\%)  &     \\ 
Region: &               & 2001\\ 
$\qquad$Southeast & 853 (42.63\%)  &     \\ 
$\qquad$South & 299 (14.94\%)  &     \\ 
$\qquad$Northeast & 521 (26.04\%)  &     \\ 
$\qquad$Center-West &  163 (8.15\%)  &     \\ 
$\qquad$North &  165 (8.25\%)  &     \\ 
High School or more: &               & 2001\\ 
$\qquad$No & 844 (42.18\%)  &     \\ 
$\qquad$Yes & 1157 (57.82\%) &     \\ 
Religion: &               & 2001\\ 
$\qquad$Catholic & 1015 (50.72\%) &     \\ 
$\qquad$Evangelical Traditional & 274 (13.69\%)  &     \\ 
$\qquad$Evangelical Pentecostal & 370 (18.49\%)  &     \\ 
$\qquad$Others/No Relig. & 342 (17.09\%)  &     \\ 
National Attachment Scale &  0.74 (0.27)  & 1918 \\ 
\hline
\end{longtable}

## Pre-treatment Balance

The pre-treatment variables in this wave were:

1. Age
2. Gender
3. Education
4. Region
5. Income
6. Religion

To have a well-balanced sample across the experiment, with demographic groups evenly distributed across them, we perform two types of balancing tests. For the continuous variables, we perform an F-test, and for the categorical variables, we run a Chi-Square test. Table \ref{baltestw1} shows that the results of these tests are insignificant (p-value above 0.10), meaning that we have a well-balanced sample across all treatment levels.

```{r, echo = FALSE}
# Age
mod <- aov(age~trstatus, data=wave1, weights = wave1$wts)
aux <- data.frame(Variable = 'Age',
                  Stat = 'F',
                  Value = round(summary(mod)[[1]][1,4], 3),
                  PValue = round(summary(mod)[[1]][1,5], 3))
# Gender
mod <- wtd.chi.sq(wave1$female, 
                  wave1$trstatus, 
                  weight = wave1$wts)
aux <- rbind(aux, data.frame(Variable = 'Gender',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))
# Education
mod <- wtd.chi.sq(wave1$hsmore, 
                  wave1$trstatus, 
                  weight = wave1$wts)
aux <- rbind(aux, data.frame(Variable = 'Education',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

# Region
mod <- wtd.chi.sq(wave1$region, 
                  wave1$trstatus, 
                  weight = wave1$wts)
aux <- rbind(aux, data.frame(Variable = 'Region',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

# Income
mod <- wtd.chi.sq(wave1$income, 
                  wave1$trstatus, 
                  weight = wave1$wts)
aux <- rbind(aux, data.frame(Variable = 'Income',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

# Religion
mod <- wtd.chi.sq(wave1$religion, 
                  wave1$trstatus, 
                  weight = wave1$wts)
aux <- rbind(aux, data.frame(Variable = 'Religion',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

names(aux) <- c('Variable', 'Statistic', 'Value', 'P-Value')
```

```{r, echo = FALSE}
aux %>%
  kable(caption = 'Pre-Treatment Balance Tests\\label{baltestw1}',
        booktabs = T) %>%
  kable_styling(latex_options = "hold_position")
```

## Treatment Effects

We begin our analysis by examining the main effects of our treatment conditions on public support for government responses to foreign shaming, which are displayed in Table \ref{mainregw1}.


```{r, echo = FALSE, results = 'asis'}
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trsource|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[3]] <- felm(
  outcbin ~ trsource*trgovresp|0|0|region,
  data = wave1, weights = wave1$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Ally Shaming', 
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Ally Shaming x Express Regret',
                               'Ally Shaming x Defy Shaming',
                               'Ally Shaming x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          title = 'Public Support for Responses to Foreign Shaming',
          label = 'mainregw1',
          align = T,
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) Adversary Shaming; (2) Remain Silent; (3) Silence upon Adversary Shaming.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}'),
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

\pagebreak

## Heterogeneous Effects -- National Attachment Scale

Table \ref{heteffw1} shows how our treatments interact with individuals based on their national attachment scale scores.

```{r, echo = FALSE, results = 'asis'}
## Heterogeneous effects
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trsource*natscale|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp*natscale|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[3]] <- felm(
  outcbin ~ trsource*trgovresp*natscale|0|0|region,
  data = wave1, weights = wave1$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Ally',
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Nat. Scale',
                               'Ally x Express Regret',
                               'Ally x Defy Shaming',
                               'Ally x Reject Shaming',
                               'Nat. Scale x Ally',
                               'Nat. Scale x Express Regret',
                               'Nat. Scale x Defy Shaming',
                               'Nat. Scale x Reject Shaming',
                               'Nat. Scale x Ally x Express Regret',
                               'Nat. Scale x Ally x Defy Shaming',
                               'Nat. Scale x Ally x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          title = 'Effects of National Attachment Scale on Public Support for Responses to Foreign Shaming',
          label = 'heteffw1',
          align = T,
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) Adversary Shaming; (2) Remain Silent; (3) Silence upon Adversary Shaming.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}'),
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

## Robustness Checks

We supplement our main analysis by running robustness checks. We add pre-treatment demographic characteristics that could potentially influence public attitudes toward foreign shaming. We add controls for education, income, gender, age, and religion. Overall, all the results remain similar to the ones presented in the main models.


```{r, echo = FALSE, results = 'asis'}
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trsource+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[3]] <- felm(
  outcbin ~ trsource*trgovresp+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave1, weights = wave1$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Ally Shaming', 
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Ally Shaming x Express Regret',
                               'Ally Shaming x Defy Shaming',
                               'Ally Shaming x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          title = 'Public Support for Responses to Foreign Shaming (pre-treatments as controls)',
          label = 'mainregw1prtr',
          align = T,
          omit = c('age', 'female', 'evang', 'more5mw', 'hsmore'),
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) Adversary Shaming; (2) Remain Silent; (3) Silence upon Adversary Shaming.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}',
                    '{\\footnotesize Control variables: Female, Age, Evangelical, More than 5 Min. Wage, and Schooling.}'),
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

```{r, echo = FALSE, results = 'asis'}
## Heterogeneous effects
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trsource*natscale+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp*natscale+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave1, weights = wave1$wts)
mod[[3]] <- felm(
  outcbin ~ trsource*trgovresp*natscale+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave1, weights = wave1$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Ally',
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Nat. Scale',
                               'Ally x Express Regret',
                               'Ally x Defy Shaming',
                               'Ally x Reject Shaming',
                               'Nat. Scale x Ally',
                               'Nat. Scale x Express Regret',
                               'Nat. Scale x Defy Shaming',
                               'Nat. Scale x Reject Shaming',
                               'Nat. Scale x Ally x Express Regret',
                               'Nat. Scale x Ally x Defy Shaming',
                               'Nat. Scale x Ally x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          omit = c('age', 'female', 'evang', 'more5mw', 'hsmore'),
          title = 'Effects of National Attachment Scale on Public Support for Responses to Foreign Shaming (pre-treatments as controls)',
          label = 'heteffw1prtr',
          align = T,
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) Adversary Shaming; (2) Remain Silent; (3) Silence upon Adversary Shaming.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}',
                    '{\\footnotesize Control variables: Female, Age, Evangelical, More than 5 Min. Wage, and Schooling.}'),
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

## Paper Figure

```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='1\\linewidth', fig.width=8, fig.height=8, fig.show='hold', fig.align='center', fig.cap='\\label{heteff}Effects of National Attachment Scale on Public Support for Responses to Foreign Shaming'}
mod <- list()
trst2 <- wave1$trstatus
levels(trst2) <- c('RSAlly','RMAlly','RCAlly','ABAlly',
                   'RSAdv','RMAdv','RCAdv','ABAdv')
trst2 <- relevel(trst2, ref = 'RSAdv')
mod[[1]] <- lm.cluster(outcbin ~ trst2*natscale, 
                 data = wave1,
                 weights = wave1$wts,
                 cluster = wave1$region)
trst2 <- relevel(trst2, ref = 'RSAlly')
mod[[2]] <- lm.cluster(outcbin ~ trst2*natscale, 
                 data = wave1,
                 weights = wave1$wts,
                 cluster = wave1$region)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RSAlly', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), 
                  Source = 'Ally')
aux <- rbind(aux,
             data.frame(
               interplot(mod[[2]]$lm_res,var1 = 'trst2RSAdv', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), 
               Source = 'Adversary')) %>%
  mutate(Source = factor(Source))

p1 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Source)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Remain Silent x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RMAdv', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), 
                  Source = 'Adversary')
aux <- rbind(aux,
             data.frame(
               interplot(mod[[1]]$lm_res,var1 = 'trst2RMAlly', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), 
                        Source = 'Ally')) %>%
  mutate(Source = factor(Source))

p2 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Source)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + 
  facet_wrap(~'Express Regret x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2ABAdv', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), Source = 'Adversary')
aux <- rbind(aux,
             data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2ABAlly', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), Source = 'Ally')) %>%
  mutate(Source = factor(Source))

p3 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Source)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Defy Shaming x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RCAdv', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), Source = 'Adversary')
aux <- rbind(aux,
             data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RCAlly', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), Source = 'Ally')) %>%
  mutate(Source = factor(Source))

p4 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Source)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Reject Shaming x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

ggarrange(p1, p2, p3, p4, ncol=2, nrow=2, common.legend = TRUE, legend="bottom")
```

\pagebreak

# Analysis Wave Two \label{sec:w2}

## Descriptive Statistics

In the wave 2 dataset (`wave2` R object), we have the following variables:

1. **`nquest`**: 9-digit DataFolha Respondent Code.
2. **`female`**: Dummy for Female Respondent.
3. **`age`**: Age.
4. **`religion`**: 4-brackets religion levels.
5. **`evang`**: Dummy for Evangelical respondent.
6. **`income`**: Income levels.
7. **`more5mw`**: Respondent More than five minimum wage salaries.
8. **`hsmore`**: Dummy for High School or more of education.
9. **`outcbin`**: Dummy for support for the governmental environmental decision.
10. **`trcontent`**: Treatment status that contrasted a control (no message) versus a liberal internationalist message.
11. **`trgovresp`**: Treatment status denoting government response to the foreign shaming.
12. **`trstatus`**: Treatment status as appeared in the survey instrument.
13. **`natscale`**: National attachment scale.
14. **`region`**: Brazilian region.
15. **`wts`**: Weights computed by the DataFolha Institute.

Our analysis comes from a sample of `r dim(wave2)[1]` Brazilian administered in January 2020 by the Datafolha Institute as part of a larger, unrelated omnibus survey. We provide a detailed explanation about the sampling methodology in the APSA Experimental Report section of this appendix. Table \ref{tab1w2ds} shows the demographic characteristics of our sample.

```{r, results = 'hide'}
aux <- wave2 %>%
  dplyr::select(age, female, income, region,
                hsmore, religion, 
                natscale) %>%
  rename(`Age` = age,
         `Female` = female,
         `Income` = income,
         `Region` = region,
         `High School or more` = hsmore,
         `Religion` = religion,
         `National Attachment Scale` = natscale)
```

```{r, results ='hide'}
export2latex(descrTable(~., digits = 2, show.p.overall = F, 
           show.all = T, data = aux))
```

\pagebreak

\begin{longtable}{lcc}\caption{Sample Characteristics}\label{tab1w2ds}\\
\hline  
&     [ALL]     & \multirow{2}{*}{ N  }\\ 
&    N=2126     &      \\ 
\hline
\hline     
\endfirsthead 
\multicolumn{3}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
\hline
&     [ALL]     & \multirow{2}{*}{ N  }\\ 
&    N=2126     &      \\ 
\hline
\hline  
\endhead   
\hline
\multicolumn{3}{l}{\textit{continued on next page}} \\ 
\endfoot   
\multicolumn{3}{l}{}  \\ 
\endlastfoot 
Age & 42.76 (16.28) & 2126\\ 
Female: &               & 2126\\ 
$\qquad$No & 1011 (47.55\%) &     \\ 
$\qquad$Yes & 1115 (52.45\%) &     \\ 
Income: &               & 2033\\ 
$\qquad$BRL 0.00 to BRL 998.00 & 411 (20.22\%)  &     \\ 
$\qquad$BRL 999.00 to BRL 1,996.00 & 527 (25.92\%)  &     \\ 
$\qquad$BRL 1,997.00 to BRL 2,994.00 & 451 (22.18\%)  &     \\ 
$\qquad$BRL 2,995.00 to BRL 4,990.00 & 353 (17.36\%)  &     \\ 
$\qquad$BRL 4,991.00 or more & 291 (14.31\%)  &     \\ 
Region: &               & 2126\\ 
$\qquad$Southeast & 900 (42.33\%)  &     \\ 
$\qquad$South & 330 (15.52\%)  &     \\ 
$\qquad$Northeast & 546 (25.68\%)  &     \\ 
$\qquad$Center-West &  177 (8.33\%)  &     \\ 
$\qquad$North &  173 (8.14\%)  &     \\ 
High School or more: &               & 2126\\ 
$\qquad$No & 920 (43.27\%)  &     \\ 
$\qquad$Yes & 1206 (56.73\%) &     \\ 
Religion: &               & 2076\\ 
$\qquad$Catholic & 1081 (52.07\%) &     \\ 
$\qquad$Evangelical Traditional & 294 (14.16\%)  &     \\ 
$\qquad$Evangelical Pentecostal & 396 (19.08\%)  &     \\ 
$\qquad$Others/No Relig. & 305 (14.69\%)  &     \\ 
National Attachment Scale &  0.73 (0.27)  & 2032 \\ 
\hline
\end{longtable}

## Pre-treatment Balance

The pre-treatment variables in this wave were:

1. Age
2. Gender
3. Education
4. Region
5. Income
6. Religion

Similarly to wave 1, in wave 2 we perform an F-test for the continuous variables and a Chi-Square test for the categorical variables. Table \ref{baltestw2} shows that the results of these tests are insignificant (p-value above 0.10), meaning that we have a well-balanced sample across all treatment levels.

```{r, echo = FALSE}
# Age
mod <- aov(age~trstatus, data=wave2, weights = wave2$wts)
aux <- data.frame(Variable = 'Age',
                  Stat = 'F',
                  Value = round(summary(mod)[[1]][1,4], 3),
                  PValue = round(summary(mod)[[1]][1,5], 3))
# Gender
mod <- wtd.chi.sq(wave2$female, 
                  wave2$trstatus, 
                  weight = wave2$wts)
aux <- rbind(aux, data.frame(Variable = 'Gender',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))
# Education
mod <- wtd.chi.sq(wave2$hsmore, 
                  wave2$trstatus, 
                  weight = wave2$wts)
aux <- rbind(aux, data.frame(Variable = 'Education',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

# Region
mod <- wtd.chi.sq(wave2$region, 
                  wave2$trstatus, 
                  weight = wave2$wts)
aux <- rbind(aux, data.frame(Variable = 'Region',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

# Income
mod <- wtd.chi.sq(wave2$income, 
                  wave2$trstatus, 
                  weight = wave2$wts)
aux <- rbind(aux, data.frame(Variable = 'Income',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

# Religion
mod <- wtd.chi.sq(wave2$religion, 
                  wave2$trstatus, 
                  weight = wave2$wts)
aux <- rbind(aux, data.frame(Variable = 'Religion',
                  Stat = 'Chi-Sq',
                  Value = round(as.numeric(mod[1]), 3),
                  PValue = round(as.numeric(mod[3]), 3)))

names(aux) <- c('Variable', 'Statistic', 'Value', 'P-Value')
```

```{r, echo = FALSE}
aux %>%
  kable(caption = 'Pre-Treatment Balance Tests \\label{baltestw2}',
        booktabs = T)  %>%
  kable_styling(latex_options = "hold_position")
```

As we can see, the results are insignificant (p-value above $0.10$) for all variables but religion. We show in the robustness checks that adding religion as a control variable does not alter our results. Under (p-value $<$ 0.1) we still have a 10\% chance of a spurious correlation between the treatment and one pre-treatment variable. For instance, in six comparison tests, under a p-value of 0.1, we have $1-(1-0.1)^6=0.469$, or 46.9\% chance of at least one test be significant at random.

Using Benjamini–Hochberg correction [@benjamini1995controlling], let $p_k$ the k-th ordered p-value, $m$ the number of tests, and $\alpha$ the significance threshold. We have to adjust the p-values using the following formula:

$$ p_k < \dfrac{k}{m}\alpha $$

When we adjust the p-values for multiple comparisons, all coefficients are insignificant.

```{r, echo = FALSE}
aux$`Adj. P-Value` = (6/rank(aux$`P-Value`))*aux$`P-Value`
aux$`Adj. P-Value`[aux$`Adj. P-Value`>1] = 1
aux %>%
  kable(caption = 'Pre-Treatment Balance Tests (with Multiple Comparison\'s Correction)\\label{baltestmcw2}', booktabs = T) %>%
  kable_styling(latex_options = "hold_position")
```

## Treatment Effects

We begin our analysis by examining the main effects of our treatment conditions on public support for government responses to foreign shaming, which are displayed in \ref{mainregw2}.

```{r, echo = FALSE, results = 'asis'}
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trcontent|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[3]] <- felm(
  outcbin ~ trcontent*trgovresp|0|0|region,
  data = wave2, weights = wave2$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Liberal Message', 
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Liberal Message x Express Regret',
                               'Liberal Message x Defy Shaming',
                               'Liberal Message x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          title = 'Public Support for Responses to the Nature of Shaming Message',
          label = 'mainregw2',
          align = T,
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) No Liberal Message (control); (2) Remain Silent; (3) Silence upon no Liberal Message.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}'),
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

## Heterogeneous Effects -- National Attachment Scale

Table \ref{heteffw2} shows how our treatments interact with individuals based on their national attachment scale scores.

```{r, echo = FALSE, results = 'asis'}
## Heterogeneous effects
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trcontent*natscale|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp*natscale|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[3]] <- felm(
  outcbin ~ trcontent*trgovresp*natscale|0|0|region,
  data = wave2, weights = wave2$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Liberal Message',
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Nat. Scale',
                               'Liberal Message x Express Regret',
                               'Liberal Message Message x Defy Shaming',
                               'Liberal Message x Reject Shaming',
                               'Nat. Scale x Liberal Message',
                               'Nat. Scale x Express Regret',
                               'Nat. Scale x Defy Shaming',
                               'Nat. Scale x Reject Shaming',
                               'Nat. Scale x Liberal Message x Express Regret',
                               'Nat. Scale x Liberal Message x Defy Shaming',
                               'Nat. Scale x Liberal Message x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          title = 'Effects of National Attachment Scale on Public Support for Responses to the Nature of Shaming Message',
          align = T,
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) No Liberal Message (control); (2) Remain Silent; (3) Silence upon No Liberal Message.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}'),
          label = 'heteffw2',
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

## Robustness Checks

We supplement our main analysis by running robustness checks. We add pre-treatment demographic characteristics that could change public attitudes toward foreign shaming. We add controls for education, income, gender, age, and religion. Overall, all the results remain similar to the ones presented in the main models.


```{r, echo = FALSE, results = 'asis'}
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trcontent+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[3]] <- felm(
  outcbin ~ trcontent*trgovresp+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave2, weights = wave2$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Liberal Message', 
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Liberal Message x Express Regret',
                               'Liberal Message x Defy Shaming',
                               'Liberal Message x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          title = 'Public Support for Responses to the Nature of Shaming Message (pre-treatments as controls)',
          label = 'mainregw2prtr',
          align = T,
          omit = c('age', 'female', 'evang', 'more5mw', 'hsmore'),
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) No Liberal Message (control); (2) Remain Silent; (3) Silence upon no Liberal Message.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}',
                    '{\\footnotesize Control variables: Female, Age, Evangelical, More than 5 Min. Wage, and Schooling.}'),
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

```{r, echo = FALSE, results = 'asis'}
## Heterogeneous effects
mod <- list()
mod[[1]] <- felm(
  outcbin ~ trcontent*natscale+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[2]] <- felm(
  outcbin ~ trgovresp*natscale+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave2, weights = wave2$wts)
mod[[3]] <- felm(
  outcbin ~ trcontent*trgovresp*natscale+female+age+evang+more5mw+hsmore|0|0|region,
  data = wave2, weights = wave2$wts)

stargazer(mod[[1]],mod[[2]],mod[[3]],
          covariate.labels = c('Liberal Message',
                               'Express Regret',
                               'Defy Shaming',
                               'Reject Shaming',
                               'Nat. Scale',
                               'Liberal Message x Express Regret',
                               'Liberal Message Message x Defy Shaming',
                               'Liberal Message x Reject Shaming',
                               'Nat. Scale x Liberal Message',
                               'Nat. Scale x Express Regret',
                               'Nat. Scale x Defy Shaming',
                               'Nat. Scale x Reject Shaming',
                               'Nat. Scale x Liberal Message x Express Regret',
                               'Nat. Scale x Liberal Message x Defy Shaming',
                               'Nat. Scale x Liberal Message x Reject Shaming',
                               'Constant'),
          type = 'latex',
          style = 'apsr',
          omit = c('age', 'female', 'evang', 'more5mw', 'hsmore'),
          title = 'Effects of National Attachment Scale on Public Support for Responses to the Nature of Shaming Message (pre-treatments as controls)',
          align = T,
          notes = c('{\\footnotesize Cluster-robust SEs in parenthesis, clustered at the Brazilian region level.}', 
                    '{\\footnotesize Reference category: (1) No Liberal Message (control); (2) Remain Silent; (3) Silence upon No Liberal Message.}',
                    '{\\footnotesize All estimates should be interpreted relative to their baseline category.}',
                    '{\\footnotesize Significance levels: $^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01}',
                    '{\\footnotesize Control variables: Female, Age, Evangelical, More than 5 Min. Wage, and Schooling.}'),
          label = 'heteffw2prtr',
          notes.append = F,
          column.sep.width = '-2pt',
          digits=3,
          keep.stat="n", 
          header = F,
          dep.var.labels.include=F)
```

## Paper Figure

```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='1\\linewidth', fig.width=8, fig.height=8, fig.show='hold', fig.align='center', fig.cap='\\label{heteff2}Effects of National Attachment Scale on Public Support for Responses to the Nature of Shaming Message.'}
mod <- list()
trst2 <- wave2$trstatus
levels(trst2) <- c('RSCtrl','RMCtrl','RCCtrl','ABCtrl',
                   'RSLib','RMLib','RCLib','ABLib')
mod[[1]] <- lm.cluster(outcbin ~ trst2*natscale, 
                 data = wave2,
                 weights = wave2$wts,
                 cluster = wave2$region)
trst2 <- relevel(trst2, ref = 'RSLib')
mod[[2]] <- lm.cluster(outcbin ~ trst2*natscale, 
                       data = wave2,
                       weights = wave2$wts,
                       cluster = wave2$region)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RSLib', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), Content = 'Liberal') %>%
  mutate(Content = factor(Content))
aux <- rbind(aux,
             data.frame(interplot(mod[[2]]$lm_res,var1 = 'trst2RSCtrl', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), Content = 'Control')) %>%
  mutate(Content = factor(Content))

p1 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Content)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Remain Silent x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RMCtrl', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), Content = 'Control')
aux <- rbind(aux,
             data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RMLib', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), Content = 'Liberal')) %>%
  mutate(Content = factor(Content))

p2 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Content)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Express Regret x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2ABCtrl', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), Content = 'Control')
aux <- rbind(aux,
             data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2ABLib', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), Content = 'Liberal')) %>%
  mutate(Content = factor(Content))

p3 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Content)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Defy Shaming x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

aux <- data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RCCtrl', 
                            var2 = 'natscale', ci = 0.95,
                            point = T, esize=1.2, plot=F), Content = 'Control')
aux <- rbind(aux,
             data.frame(interplot(mod[[1]]$lm_res,var1 = 'trst2RCLib', 
                                  var2 = 'natscale', ci = 0.95,
                                  point = T, esize=1.2, plot=F), Content = 'Liberal')) %>%
  mutate(Content = factor(Content))

p4 <- aux %>%
  mutate(natscale = round(natscale, 2)) %>%
  ggplot(aes(x = as.factor(natscale), y = coef, colour = Content)) +
  geom_errorbar(aes(x = as.factor(natscale), y = coef,
                    ymin = lb, 
                    ymax = ub), width = 0.2,
                position=position_dodge(0.4)) +
  geom_point(position=position_dodge(0.4)) + 
  geom_hline(yintercept=0, linetype="dashed") +
  theme_bw() + facet_wrap(~'Reject Shaming x\nNat. Attachment Scale') +
  xlab('') + scale_color_manual(values=c("red", "blue")) +
  ylab('') + ylim(-1.01,1.01)

ggarrange(p1, p2, p3, p4, ncol=2, nrow=2, common.legend = TRUE, legend="bottom")
```

\pagebreak

# APSA Experimental Section Report

## Hypothesis

- What are the questions the experiment was designed to address?

  + In these two-wave survey, we studied the XXXX.

-	What are the specific hypotheses to be tested?

    + We are testing whether respondents in a XXXX.

##	Subjects and Context

-	Who was eligible to participate in the study?

    + The target population is comprised of Brazilian citizens over 18 years of age.

- What would result in the exclusion of a participant?

    + Being a foreigner, or younger than 18 years old.

- Procedures used to recruit and select participants
  + The survey company sampled municipalities to match the demographic composition laid out by the national census alongside age, income, education, gender, and region. We used the 2018 quota published by the Brazilian Institute of Geography and Statistics (IBGE) as a reference. Moreover, the survey company allocated enumerators in strategic places with a large influx of people. Around 30 percent of responses were double-checked for consistency.

- Recruitment dates defining the periods of recruitment and when the experiments were conducted.
  + The first and second wave of the experiment occurred between January 13 and January 17, 2020. As this was a face-to-face survey experiment, enumerators recruited respondents at the street level.

- Dates of any repeated
  + Not applicable.

- Settings and locations where the data were collected
  + Enumerators were distributed in approximately 120 municipalities which were randomly selected by a stratum of the region, nature of the municipality (state capital, other metropolitan or interior regions), federal state, and municipality population size. The DataFolha Institute selected municipalities on the basis of the 2018 Brazilian Demographic Census and the population projections issued that year by the Brazilian Institute of Geography and Statistics (IBGE). Enumerators collected the data face-to-face.

- Where? Field? Lab? Etc.
  + Face-to-face survey.

- Survey: Response rate and how it was calculated
  + The first survey wave had `r nrow(wave1)` respondents, and the second wave had a response rate of `r nrow(wave2)`. The company did not supply data on attrition levels during the survey.

## Allocation Methods

- Details of the procedure used to generate the assignment sequence (randomization procedure)
  + We use cluster random assignment, randomizing the vignette of the experiment within each survey quota.
  + There were `r length(table(wave1$trstatus))` treatment arms in the first wave. The answers ranged from `r as.numeric(min(table(wave1$trstatus)))` to `r as.numeric(max(table(wave1$trstatus)))` participants in each treatment status. In the second wave, there were `r length(table(wave2$trstatus))` treatment arms. The answers ranged from `r as.numeric(min(table(wave2$trstatus)))` to `r as.numeric(max(table(wave2$trstatus)))` participants in each treatment status.

- Random assignment
  + Simple random assignment within the region quota.
  

- Units of randomization
  + The randomization was performed within region quota at the respondent's level.

- Cluster random assignment
  + Region. We use cluster-robust standard error, with Region as the cluster.

- Evidence for random assignment
  + We checked pre-treatment imbalance between control and the treatments in all the following variables: age, gender, education, region, income, and religion.

- Pre-treatment variables
  + We have six pre-treatment variables:
    + Age
    + Gender
    + Education
    + Region
    + Income
    + Religion

- Characteristics of the population
  + The groups of respondents are representative of the entire Brazilian population based on the 2010 national census including age, income, education, gender, and region issued  by the Brazilian Institute of Geography and Statistics (IBGE).

- Block randomization
  + We did not use block randomization.

- Blinding: Were participants unaware of the treatment assignment?
  + Yes. The randomization had an equal chance of drawing any of the vignettes for any given respondent. Respondents could not foresee which vignette would be drawn nor could they see there was more than one vignette for each question. Moreover, the enumerators administering the survey did not inform the experimental nature of the research before the application of the instrument.

- Were those administering the intervention unaware of the random assignment?
  + No. The enumerators were informed about the random nature of the study and trained to read each of the vignette questions that showed up on their tablets without revealing the experimental nature of the research.

- Checked whether blind was successful?
  + Not applicable.

## Treatments

- Descriptions of the intervention:
  + The intervention will consist of three steps.
    + Step 1: Collecting information on the extent to which the respondents agree or disagree with two statements that tap into a national attachment scale.
    + Step 2: Applying the survey experiment.
    + Step 3: Collecting standard demographic characteristics.

- Describe the treatment and control groups
  + In the first wave of the survey experiment we assigned each respondent to one of the eight treatments. All respondents heard a hypothetical situation in which Brazil suffered shaming accusations by a foreign actor for poorly managing fires and deforestation in the Amazon forest. We then randomized the source of criticism – ally and friend and adversary. Finally, we randomized all four possible reactions to shaming: silence, regret, rejection, and defiance. All the treatment conditions are outlined below.
    + Treatment 1: Ally shaming, Remain silent.
    + Treatment 2: Ally shaming, Express regret.
    + Treatment 3: Ally shaming, Reject shaming.
    + Treatment 4: Ally shaming, Defy shaming.
    + Treatment 5: Adversary shaming, Remain silent
    + Treatment 6: Adversary shaming, Express regret.
    + Treatment 7: Adversary shaming, Reject shaming.
    + Treatment 8: Adversary shaming, Defy shaming.

  + In the second wave of the experiment we assigned each respondent to either the control condition or one of the treatment conditions. All respondents continued to hear about a hypothetical situation in which Brazil suffered shaming accusations by a foreign actor for poorly managing fires and deforestation in the Amazon forest. While we mentioned that shaming came from a foreign country, we did not specify whether it is an ally or an adversary. However, we varied whether criticism was couched in liberal internationalist language or no information about the nature of criticism was provided. The range of possible responses to shaming continued to vary in terms of silence, regret, rejection, and defiance.

    + Treatment 1: Foreign country shaming, Remain silent.
    + Treatment 2: : Foreign country shaming, Express regret.
    + Treatment 3: Foreign country shaming, Reject shaming.
    + Treatment 4: Foreign country shaming, Defy shaming.
    + Treatment 5: Foreign country shaming, Liberal internationalist message, Remain silent.
    + Treatment 6: Foreign country shaming, Liberal Internationalist message, Express regret.
    + Treatment 7: Foreign country shaming, Liberal Internationalist message, Reject shaming.
    + Treatment 8: Foreign country shaming, Liberal Internationalist message, Defy shaming.

- Experimental instructions
  + To introduce the experimental question, the enumerator reads the following instructions:
“*Everyone talks about wildfires and deforestation in the Amazon forest. We will read some imaginary scenarios and ask what you think of each*”. Then the enumerator asks the questions.

- How and when manipulations were administered
  + The manipulation will be applied after the measurement of step one (see above), but before the measurement of the demographic variables.

- Method of delivery
  + The delivery was made by the enumerator reading the randomly-selected experimental vignette to the respondent.

- Software used to administer the treatment
  + DataFolha Institute uses the SurveyToGo software on their tablets. Respondents also read cards with the description of the control or one of the treatment conditions.

## Results

### Outcome measures and covariates

- Outcome measures
  + The outcome measured in both waves is the level of support for different responses to foreign shaming.

- Covariates
  + We use the variables age, income, education, gender, religion, race, and religion as **pre-treatment covariates**.

- Survey Questionnaires
  + First Wave: [English translation](https://github.com/umbertomig/environmental-politics-survey/blob/master/appendix/survey_instruments/wave1.pdf).
  + Second Wave: [English translation](https://github.com/umbertomig/environmental-politics-survey/blob/master/appendix/survey_instruments/wave2.pdf).

- Which outcomes and subgroup analysis were specified prior to the experiment?
  + In the paper, we use a **national attachment scale** to measure heterogeneous effects at the individual level. Items are drawn from previous work on national attachment [@herrmann2017attachments; @rathbun2019moral; @bayram2017due]. In particular, we test how individuals scoring differently in national attachment on a values scale interact with our treatment conditions. The national attachment scale consists of a combination of the following two questions.
    + “*When someone says something bad about Brazil, you feel it is as if they say something bad about you.*”
    + “*Brazil should stand for national honor, even if it compromises its image in the world.*”
    + The response options for each item are “agree totally,” “agree partially,” “neither agree or disagree,” “disagree partially,” and “disagree totally.”

- Exploratory analysis? What find?
  + No exploratory analysis has been run.

### CONSORT

- Number of subjects initially accessed for eligibility:
    + We fielded a sample of 2001 and 2126 respondents in wave 1 and wave 2, respectively.

- Exclusions prior to random assignment
     + There were no exclusions.

- Subjects initially assigned to each experimental group
  + In the first wave:
    + Treatment 1 (Ally shaming, Remain silent): `r as.numeric(table(wave1$trstatus)[1])` respondents.
    + Treatment 2 (Ally shaming, Express regret): `r as.numeric(table(wave1$trstatus)[2])` respondents.
    + Treatment 3 (Ally shaming, Reject shaming): `r as.numeric(table(wave1$trstatus)[3])` respondents.
    + Treatment 4 (Ally shaming, Defy shaming): `r as.numeric(table(wave1$trstatus)[4])` respondents.
    + Treatment 5 (Adversary shaming, Remain silent): `r as.numeric(table(wave1$trstatus)[5])` respondents.
    + Treatment 6 (Adversary shaming, Express regret): `r as.numeric(table(wave1$trstatus)[6])` respondents.
    + Treatment 7 (Adversary shaming, Reject shaming): `r as.numeric(table(wave1$trstatus)[7])` respondents.
    + Treatment 8 (Adversary shaming, Defy shaming): `r as.numeric(table(wave1$trstatus)[8])` respondents.

  + In the second wave:
    + Treatment 1 (Foreign country shaming, Remain silent): `r as.numeric(table(wave2$trstatus)[1])` respondents.
    + Treatment 2 (Foreign country shaming, Express regret): `r as.numeric(table(wave2$trstatus)[2])` respondents.
    + Treatment 3 (Foreign country shaming, Reject shaming): `r as.numeric(table(wave2$trstatus)[3])` respondents.
    + Treatment 4 (Foreign country shaming, Defy shaming): `r as.numeric(table(wave2$trstatus)[4])` respondents.
    + Treatment 5 (Foreign country shaming, Liberal Internationalist message, Remain silent): `r as.numeric(table(wave2$trstatus)[5])` respondents.
    + Treatment 6 (Foreign country shaming, Liberal Internationalist message, Express regret): `r as.numeric(table(wave2$trstatus)[6])` respondents.
    + Treatment 7 (Foreign country shaming, Liberal Internationalist message, Reject shaming): `r as.numeric(table(wave2$trstatus)[7])` respondents.
    + Treatment 8 (Foreign country shaming, Liberal Internationalist message, Defy shaming): `r as.numeric(table(wave2$trstatus)[8])` respondents.

- Proportion received x not received intervention:
  + In the first wave:
    + Treatment 1 (Ally shaming, Remain silent): `r round(as.numeric(prop.table(table(wave1$trstatus)))[1]*100,2)` percent.
    + Treatment 2 (Ally shaming, Express regret): `r round(as.numeric(prop.table(table(wave1$trstatus)))[2]*100,2)` percent.
    + Treatment 3 (Ally shaming, Reject shaming): `r round(as.numeric(prop.table(table(wave1$trstatus)))[3]*100,2)` percent.
    + Treatment 4 (Ally shaming, Defy shaming): `r round(as.numeric(prop.table(table(wave1$trstatus)))[4]*100,2)` percent.
    + Treatment 5 (Adversary shaming, Remain silent): `r round(as.numeric(prop.table(table(wave1$trstatus)))[5]*100,2)` percent.
    + Treatment 6 (Adversary shaming, Express regret): `r round(as.numeric(prop.table(table(wave1$trstatus)))[6]*100,2)` percent.
    + Treatment 7 (Adversary shaming, Reject shaming): `r round(as.numeric(prop.table(table(wave1$trstatus)))[7]*100,2)` percent.
    + Treatment 8 (Adversary shaming, Defy shaming): `r round(as.numeric(prop.table(table(wave1$trstatus)))[8]*100,2)` percent.

  + In the second wave:
    + Treatment 1 (Foreign country shaming, Remain silent): `r round(as.numeric(prop.table(table(wave2$trstatus)))[1]*100,2)` percent.
    + Treatment 2 (Foreign country shaming, Express regret): `r round(as.numeric(prop.table(table(wave2$trstatus)))[2]*100,2)` percent.
    + Treatment 3 (Foreign country shaming, Reject shaming): `r round(as.numeric(prop.table(table(wave2$trstatus)))[3]*100,2)` percent.
    + Treatment 4 (Foreign country shaming, Defy shaming): `r round(as.numeric(prop.table(table(wave2$trstatus)))[4]*100,2)` percent.
    + Treatment 5 (Foreign country shaming, Liberal Internationalist message, Remain silent): `r round(as.numeric(prop.table(table(wave2$trstatus)))[5]*100,2)` percent.
    + Treatment 6 (Foreign country shaming, Liberal Internationalist message, Express regret): `r round(as.numeric(prop.table(table(wave2$trstatus)))[6]*100,2)` percent.
    + Treatment 7 (Foreign country shaming, Liberal Internationalist message, Reject shaming): `r round(as.numeric(prop.table(table(wave2$trstatus)))[7]*100,2)` percent.
    + Treatment 8 (Foreign country shaming, Liberal Internationalist message, Defy shaming): `r round(as.numeric(prop.table(table(wave2$trstatus)))[8]*100,2)` percent.

- Why did not receive intervention?
    + The study is a case-control study.

- Number subjects each group dropped experiment
    + No respondent was dropped.

- Number included and any reason for exclusion
    + Not applicable.

### Statistical analysis

- Describe statistical analysis
  + Linear regression analysis (OLS) with cluster-robust standard errors. We used the function `felm` from the package `lfe` in R. The package provides a straightforward way to estimate cluster-robust standard errors.

\newpage

- Means and standard deviations
  
  + For the first wave:
  
```{r, w1means}
wave1 %>% 
  group_by(trstatus) %>%
  summarise(`Mean Support` = round(mean(outcbin, na.rm=T), 3),
            `SD Suppor` = round(sd(outcbin, na.rm=T), 3),
            `SE Support` = round(sd(outcbin, na.rm=T)/sqrt(n()), 3)) %>%
  data.frame() %>%
  mutate(trstatus = gsub('Recognize Mistakes', 
                         'Express regret', 
                         trstatus)) %>%
  mutate(trstatus = gsub('Reject Criticisms', 
                         'Reject Shaming', 
                         trstatus)) %>%
  mutate(trstatus = gsub('Abandon International Treaties', 
                         'Defy Shaming', 
                         trstatus)) %>%
  kable(booktabs = T)  %>%
  kable_styling(latex_options = c("hold_position"))
```
    + For the second wave:
  
```{r w2means, echo = FALSE}
wave2 %>% 
  group_by(trstatus) %>%
  summarise(`Mean Support` = round(mean(outcbin, na.rm=T), 3),
            `SD Support` = round(sd(outcbin, na.rm=T), 3),
            `SE Support` = round(sd(outcbin, na.rm=T)/sqrt(n()), 3)) %>%
  data.frame() %>%
  mutate(trstatus = gsub('Recognize Mistakes', 
                         'Express regret', 
                         trstatus)) %>%
  mutate(trstatus = gsub('Reject Criticisms', 
                         'Reject Shaming', 
                         trstatus)) %>%
  mutate(trstatus = gsub('Abandon International Treaties', 
                         'Defy Shaming', 
                         trstatus)) %>%
  mutate(trstatus = gsub('Amazon belongs to all humankind', 
                         'Liberal Message', 
                         trstatus)) %>%
  kable(booktabs = T)  %>%
  kable_styling(latex_options = c("hold_position"))
```

- ITT
  + Not applicable.

- If use block randomization, ITT by block or overall means using IPW
  + Not applicable.

- Standard errors:
  
  + Cluster-robust standard errors, clustering at the Region level.

- Attrition:
  
  + Not applicable.

- Analyze pre-treatment variables to check reasons
  
  + See the pre-treatment balance section.

- Missing data
  
  + Most of the missing is generated by the `Don't know` answer in the primary outcomes. This was a voluntary answer that affected `r sum(is.na(wave1$outcbin))` out of `r nrow(wave1)` responses in the first wave, and `r sum(is.na(wave2$outcbin))` out of `r nrow(wave2)` responses in the second wave.

- Frequency and percentage missing by group
  + See the descriptive statistics section for each of the waves.

- Method for addressing missing data
  + Not applicable.

\newpage

- Summary missing data by subgroup
  + For the first wave:
```{r w1miss, echo = FALSE}
tab <- table(wave1$trstatus, is.na(wave1$outcbin))
colnames(tab) <- c('Valid', 'Missing')
row.names(tab) <- gsub('Recognize Mistakes', 
                       'Express regret', 
                       row.names(tab))
row.names(tab) <- gsub('Reject Criticisms', 
                       'Reject Shaming', 
                       row.names(tab))
row.names(tab) <- gsub('Abandon International Treaties', 
                       'Defy Shaming',
                       row.names(tab))
tab %>%
  kable(booktabs = T)  %>%
  kable_styling(latex_options = c("hold_position"))
```
  - For the second wave:
```{r w2miss, echo = F}
tab <- table(wave2$trstatus, is.na(wave2$outcbin))
colnames(tab) <- c('Valid','Missing')
row.names(tab) <- gsub('Recognize Mistakes', 
                       'Express regret', 
                       row.names(tab))
row.names(tab) <- gsub('Reject Criticisms', 
                       'Reject Shaming', 
                       row.names(tab))
row.names(tab) <- gsub('Abandon International Treaties', 
                       'Defy Shaming',
                       row.names(tab))
row.names(tab) <- gsub('Amazon belongs to all humankind', 
                       'Liberal Message',
                       row.names(tab))
tab %>%
  kable(booktabs = T)  %>%
  kable_styling(latex_options = c("hold_position"))
```

\newpage

- Survey experiments:
  + A histogram of the weights for the wave 1 follows below.
  
```{r, fig.pos='h'}
hist(wave1$wts, main = 'Weights Wave 1', xlab = 'Weights')
```
  
  + A histogram of the weights for the wave 2 follows below.
  
```{r, fig.pos='h'}
hist(wave2$wts, main = 'Weights Wave 2', xlab = 'Weights')
```

- Reweighing procedures
  + We only use the weights assigned by the DataFolha Institute. The weights assigned by DataFolha have the purpose of guarantee the representativeness of the Brazilian population.

## Other information

- IRB
  + This study received IRB approval number 124/2019 from the FGV Ethics Committee (CEPH-FGV) on October 18, 2019.

- Pre-registered? Where?
  + This experiment has not being pre-registered.

- Funding? Role of funders in the experiment?
  + FGV. No funder interfered neither in the design nor in the implementation of this experiment.

- Replication dataset? URL?
  + The replication data is in the following GitHub repository: [https://github.com/umbertomig/environmental-politics-survey](https://github.com/umbertomig/environmental-politics-survey).

## Session Information

We use `r R.version.string` to write this appendix. For the regression models estimation, we use the package `lfe`. Everything in this report is fully automated and can be reproduced using R Markdown.

```{r}
sessionInfo()
```